\texttt{Taxonomic supertree construction with}\texttt{\emph{ Incertae sedis}}\texttt{ taxa}

### 2018-05-03 doc/incertae_sedis.tex
compiles

\section{Placements}
\textbf{Whale:}~ ?ott6145835~{[}6145835~Brandtocetus/genus{]}~<-~ott69
8424~{[}698424~Cetacea/orde r{]}~placed~under~ott4942423~{[}4942423~Ce
totherium~/~genus{]}~<-~ott698424~{[}6 98424~Cetacea/order{]}

\textbf{Whale:}~?ott6145873~{[}6145873{]}~<-~ott698424~{[}698424~Cetac
\ea~/~order
\{]}~placed~under~ott4942423~{[}4942423{]}~<-~ott698424~{[}698424{]}~

@@

\textbf{Insect:}~?ott18090~{[}18090{]}~<-~ott672501~{[}672501{]}~place
\d~under~ot t275501~{[}275501{]}~<-~ott672501~{[}672501{]}

\textbf{Insect:}~?ott190269~{[}190269{]}~<-~ott672501~{[}672501{]}~pla
\ced~under~ ott275501~{[}275501{]}~<-~ott672501~{[}672501{]}~

\textbf{Insect:}~?ott349638~{[}349638{]}~<-~ott672501~{[}672501{]}~pla
\ced~under~ ott275501~{[}275501{]}~<-~ott672501~{[}672501{]}~

\textbf{Insect:}~?ott1009313~{[}1009313{]}~<-~ott672501~{[}672501~Redu
\viidae~/~f amily{]}~placed~under~ott275501~{[}275501{]}~<-~ott672501~
\{[}672501{]}~

@@

\textbf{Insect:~}?ott564110~{[}564110{]}~<-~ott939130~{[}939130~Thyrid
\idae~/~fam
\ily{]}~placed~under~ott757344~{[}757344{]}~<-~ott939130~{[}939130{]}~

\textbf{Plant:}~?ott679485~{[}679485{]}~<-~ott1074933~{[}1074933~Lamio
\idea~/~sub family{]}~placed~under~ott534796~{[}534796{]}~<-~

\textbf{Plant:}~?ott729184~{[}729184{]}~<-~ott1074933~{[}1074933~Lamio
\idea~/~sub family~{]}~placed~under~ott534796~{[}534796{]}~<-~ott10749
\33~{[}1074933{]}~

@@

\textbf{Plant:}~?ott5144555~{[}5144555{]}~<-~ott23373~{[}23373{]}~plac
\ed~under~o tt447802~{[}447802{]}~<-~ott23373~{[}23373{]}

@@

\textbf{Fly:}~?ott441413~{[}441413~Rhodesiella~lungliensis/species{]}~
\<-~ott1014 022~{[}1014022~Rubiaceae{]}~placed~under~ott571842~{[}5718
\42~Pavetteae~/~tribe{ ]}~<-~ott997381~{[}997381~Ixoroidea/subfamily{]
\}~<-~ott1014022~{[}1014022~Rubia ceae/family{]}

\textbf{Plant:}~?ott31033~{[}31033{]}~<-~ott627035~{[}627035{]}~placed
\~under~ott 6019314~{[}6019314{]}~<-~ott627035~{[}627035{]}~

\textbf{Bacteria:}~?ott4018918~{[}4018918{]}~<-~ott5248084~{[}5248084{
\]}~placed~ under~ott167767~{[}167767{]}~<-~ott5248084~{[}5248084{]}~

\textbf{Bacteria:}?ott4792759~{[}4792759{]}~<-~ott5248084~{[}5248084{]
\}~placed~u nder~ott167767~{[}167767{]}~<-~ott5248084~{[}5248084{]}~

>>>>

\section{Placements}
\textbf{Whale:}~ ?ott6145835~{[}6145835~Brandtocetus/genus{]}~<-~ott698424~{[}698424~Cetacea/orde r{]}~placed~under~ott4942423~{[}4942423~Cetotherium~/~genus{]}~<-~ott698424~{[}6 98424~Cetacea/order{]}

\textbf{Whale:}~?ott6145873~{[}6145873{]}~<-~ott698424~{[}698424~Cetacea~/~order{]}~placed~under~ott4942423~{[}4942423{]}~<-~ott698424~{[}698424{]}~

@@

\textbf{Insect:}~?ott18090~{[}18090{]}~<-~ott672501~{[}672501{]}~placed~under~ot t275501~{[}275501{]}~<-~ott672501~{[}672501{]}

\textbf{Insect:}~?ott190269~{[}190269{]}~<-~ott672501~{[}672501{]}~placed~under~ ott275501~{[}275501{]}~<-~ott672501~{[}672501{]}~

\textbf{Insect:}~?ott349638~{[}349638{]}~<-~ott672501~{[}672501{]}~placed~under~ ott275501~{[}275501{]}~<-~ott672501~{[}672501{]}~

\textbf{Insect:}~?ott1009313~{[}1009313{]}~<-~ott672501~{[}672501~Reduviidae~/~f amily{]}~placed~under~ott275501~{[}275501{]}~<-~ott672501~{[}672501{]}~

@@

\textbf{Insect:~}?ott564110~{[}564110{]}~<-~ott939130~{[}939130~Thyrididae~/~family{]}~placed~under~ott757344~{[}757344{]}~<-~ott939130~{[}939130{]}~

\textbf{Plant:}~?ott679485~{[}679485{]}~<-~ott1074933~{[}1074933~Lamioidea~/~sub family{]}~placed~under~ott534796~{[}534796{]}~<-~

\textbf{Plant:}~?ott729184~{[}729184{]}~<-~ott1074933~{[}1074933~Lamioidea~/~sub family~{]}~placed~under~ott534796~{[}534796{]}~<-~ott1074933~{[}1074933{]}~

@@

\textbf{Plant:}~?ott5144555~{[}5144555{]}~<-~ott23373~{[}23373{]}~placed~under~o tt447802~{[}447802{]}~<-~ott23373~{[}23373{]}

@@

\textbf{Fly:}~?ott441413~{[}441413~Rhodesiella~lungliensis/species{]}~<-~ott1014 022~{[}1014022~Rubiaceae{]}~placed~under~ott571842~{[}571842~Pavetteae~/~tribe{ ]}~<-~ott997381~{[}997381~Ixoroidea/subfamily{]}~<-~ott1014022~{[}1014022~Rubia ceae/family{]}

\textbf{Plant:}~?ott31033~{[}31033{]}~<-~ott627035~{[}627035{]}~placed~under~ott 6019314~{[}6019314{]}~<-~ott627035~{[}627035{]}~

\textbf{Bacteria:}~?ott4018918~{[}4018918{]}~<-~ott5248084~{[}5248084{]}~placed~ under~ott167767~{[}167767{]}~<-~ott5248084~{[}5248084{]}~

\textbf{Bacteria:}?ott4792759~{[}4792759{]}~<-~ott5248084~{[}5248084{]}~placed~u nder~ott167767~{[}167767{]}~<-~ott5248084~{[}5248084{]}~
